---
title: "Analysis Of Fund dongfanghong"
author: "Wu Wei"
date: "2017-9-7"
output: html_document
---



## 1 Library input & Data Input
```{r, eval=TRUE}
suppressMessages(library(forecast))
suppressMessages(library(ggplot2))
suppressMessages(library(rugarch))
suppressMessages(library(lmtest))
suppressMessages(library(tseries))
suppressMessages(library(fBasics))

suppressMessages(library("FinTS"))
```

```{r source, echo = FALSE}
source("d://MyR//zhao//ComputeMarketModel.R")
source("d://MyR//zhao//ComputeTMModel.R")
source("d://MyR//zhao//ComputeHMModel.R")
```

```{r, eval=TRUE}
setwd("d://MyR//dongfanghong//")
dongfanghong.original.data <- read.csv("dongfanghongmonthlyjingzhi.csv")
# (original.data)

dongfanghong.close.price <- ts(dongfanghong.original.data[,2], start = c(2015, 7), frequency = 12)

money.interest <- ts(dongfanghong.original.data[,3], start = c(2015, 7), frequency = 12)
hushen300.price <- ts(dongfanghong.original.data[,4], start = c(2015, 7), frequency = 12)
zz500.price <- ts(dongfanghong.original.data[,5], start = c(2015, 7), frequency = 12)
zz800.price <- ts(dongfanghong.original.data[,6], start = c(2015, 7), frequency = 12)
szhl.price <- ts(dongfanghong.original.data[,7], start = c(2015, 7), frequency = 12)
```

```{r}
dongfanghong.monthly.return <- ts(diff(log(dongfanghong.close.price)), start = c(2015,8), frequency = 12)

hushen300.monthly.return <- diff(log(hushen300.price))

zz500.monthly.return <- diff(log(zz500.price))

zz800.monthly.return <- diff(log(zz800.price))

szhl.monthly.return <- diff(log(szhl.price))

money.monthly.interest <- ts(log(1 + (money.interest[-1] / 12)),start = c(2015, 8), frequency = 12)
```

```{r}
hushen300.monthly.return.no.risk <- ts(round(as.numeric(hushen300.monthly.return - money.monthly.interest) * 100, 
                                              digits = 2), 
                                       start = c(2015, 8), frequency = 12)

zz500.monthly.return.no.risk <- ts(round(as.numeric(zz500.monthly.return - money.monthly.interest) * 100, 
                                              digits = 2), 
                                       start = c(2015, 8), frequency = 12)

zz800.monthly.return.no.risk <- ts(round(as.numeric(zz800.monthly.return - money.monthly.interest) * 100, 
                                              digits = 2), 
                                       start = c(2015, 8), frequency = 12)

szhl.monthly.return.no.risk <- ts(round(as.numeric(szhl.monthly.return - money.monthly.interest) * 100, 
                                              digits = 2), 
                                       start = c(2015, 8), frequency = 12)

dongfanghong.monthly.return.no.risk <- ts(round(as.numeric((dongfanghong.monthly.return - money.monthly.interest) * 100),
                                     digits = 2),start = c(2015, 8), frequency = 12)

```


```{r, eval=TRUE}
zhao.original.data <- read.csv("d://MyR//zhao//zhao.csv")
zhao.close.price <- as.ts(zhao.original.data[,2])

```

```{r}
zhao.monthly.return <- diff(log(zhao.close.price))
```

```{r}
dongfanghong.yearly.return <- diff(log(dongfanghong.close.price), lag = 12)
```


## 2 Analysis for monthly return
```{r, eval=TRUE}


# date <- as.character(dongfanghong.original.data$X)

# names(dongfanghong.monthly.return) <- date[-c(1,length(date))]



plot(dongfanghong.monthly.return, type = "l")

abline(h = 0, col = "red")
```

```{r, eval=TRUE}

ndiffs(dongfanghong.monthly.return)

```

```{r, fig.height=8, fig.width=10}

tsdisplay(dongfanghong.monthly.return)

```



```{r, eval=TRUE}
mean(dongfanghong.monthly.return)

mean(dongfanghong.monthly.return) * 12

sd(dongfanghong.monthly.return)

sd(dongfanghong.monthly.return) * sqrt(12)

quantile(dongfanghong.monthly.return, c(0.05, seq(0,1,0.25)))

skewness(dongfanghong.monthly.return)
kurtosis(dongfanghong.monthly.return)
jarqueberaTest(dongfanghong.monthly.return)


```


```{r, eval=TRUE}


cor(dongfanghong.monthly.return, 
    tail(zhao.monthly.return, length(dongfanghong.monthly.return)))


```

## 3.  Analysis of monthly return between dongfanghong and hushen300 with money interest subtracted

### 3.1 Analysis of total data


```{r}
cor(hushen300.monthly.return.no.risk, dongfanghong.monthly.return.no.risk)

cor(hushen300.monthly.return.no.risk, zz500.monthly.return.no.risk)
cor(hushen300.monthly.return.no.risk, szhl.monthly.return.no.risk)
cor(szhl.monthly.return.no.risk, zz500.monthly.return.no.risk)
```

```{r}
fit.0 <- lm(zz800.monthly.return.no.risk ~ hushen300.monthly.return.no.risk + 
                    zz500.monthly.return.no.risk)

summary(fit.0)
```


```{r}
fit <- lm(dongfanghong.monthly.return.no.risk ~ hushen300.monthly.return.no.risk)

summary(fit)
```

```{r}

fit.2 <- lm(dongfanghong.monthly.return.no.risk ~ hushen300.monthly.return.no.risk + zz500.monthly.return.no.risk)

summary(fit.2)
```

```{r}

fit.3 <- lm(dongfanghong.monthly.return.no.risk ~ zz800.monthly.return.no.risk)

summary(fit.3)
```

```{r}

fit.4 <- lm(dongfanghong.monthly.return.no.risk ~ zz500.monthly.return.no.risk)

summary(fit.4)
```

```{r}

fit.5 <- lm(dongfanghong.monthly.return.no.risk ~ szhl.monthly.return.no.risk)

summary(fit.5)
```

```{r}

fit.6 <- lm(dongfanghong.monthly.return.no.risk ~ zz500.monthly.return.no.risk + szhl.monthly.return.no.risk)

summary(fit.6)
```

```{r, fig.height=6, fig.width=8}
plot(as.numeric(hushen300.monthly.return.no.risk), 
     as.numeric(dongfanghong.monthly.return.no.risk), 
     type = "p", 
     xlab = "沪深300月度超额收益率%", 
     ylab = "东方红京东大数据月度超额收益率%", 
     main = "证券特征线")

abline(h = 0, v = 0, col = "green")
points(tail(hushen300.monthly.return.no.risk), tail(dongfanghong.monthly.return.no.risk), col = "purple", pch = 20)

abline(fit)

```

### 3.1.1 Analysis of total data using TM model
```{r}
hushen300.monthly.return.square <- hushen300.monthly.return.no.risk^2

fit.tm <- lm(dongfanghong.monthly.return.no.risk ~ hushen300.monthly.return.no.risk + 
                     hushen300.monthly.return.square)

summary(fit.tm)
```

### 3.1.2 Analysis of total data using HM model
```{r}

hushen300.monthly.return.positive <- hushen300.monthly.return.no.risk
hushen300.monthly.return.positive[hushen300.monthly.return.positive < 0] <- 0

fit.hm <- lm(dongfanghong.monthly.return.no.risk ~ hushen300.monthly.return.no.risk + 
                     hushen300.monthly.return.positive)

summary(fit.hm)
```

### 3.2 Analysis of moving 12 months data

```{r}
alpha <- ts(rep(0,length(dongfanghong.monthly.return.no.risk)), start = c(2015, 8), frequency = 12)
beta <- alpha
gamma <- alpha

return.matrix.tm <- cbind(dongfanghong.monthly.return.no.risk, 
                       hushen300.monthly.return.no.risk, 
                       alpha, 
                       beta,
                       gamma) 

dimnames(return.matrix.tm)[[2]][1] <- "dongfanghong"
dimnames(return.matrix.tm)[[2]][2] <- "hushen300"

return.matrix.hm <- return.matrix.tm

return.matrix <- return.matrix.tm[,1:4]
```

```{r}
(return.matrix <- ComputeMarketModel(return.matrix))
```

```{r, fig.height=10, fig.width=10}
plot.layout.matrix <- matrix(c(1,2,3), 
                             nr = 3,
                             byrow = TRUE)

layout(plot.layout.matrix)

plot(return.matrix[,"dongfanghong"])
abline(h = 0, col = "green")

plot(return.matrix[,"alpha"])
abline(h = 0, col = "green")

plot(return.matrix[,"beta"])
abline(h = 0, col = "green")

layout(matrix(1))
```

#### 3.2.1 Analysis of moving 12 months data using TM model


```{r}
(return.matrix.tm <- ComputeTMModel(return.matrix.tm))
```

```{r, fig.height=12, fig.width=10}
plot.layout.matrix <- matrix(c(1,2,3,4), 
                             nr = 4,
                             byrow = TRUE)

layout(plot.layout.matrix)

plot(return.matrix.tm[,"dongfanghong"])
abline(h = 0, col = "green")

plot(return.matrix.tm[,"alpha"])
abline(h = 0, col = "green")

plot(return.matrix.tm[,"beta"])
abline(h = 0, col = "green")

plot(return.matrix.tm[,"gamma"])
abline(h = 0, col = "green")

layout(matrix(1))
```

#### 3.2.2 Analysis of moving 12 months data using HM model


```{r}
(return.matrix.hm <- ComputeHMModel(return.matrix.hm))
```

```{r, fig.height=12, fig.width=10}
plot.layout.matrix <- matrix(c(1,2,3,4), 
                             nr = 4,
                             byrow = TRUE)

layout(plot.layout.matrix)

plot(return.matrix.hm[,"dongfanghong"])
abline(h = 0, col = "green")

plot(return.matrix.hm[,"alpha"])
abline(h = 0, col = "green")

plot(return.matrix.hm[,"beta"])
abline(h = 0, col = "green")

plot(return.matrix.hm[,"gamma"])
abline(h = 0, col = "green")

layout(matrix(1))
```


## 4 Analysis for yearly return

```{r, eval=TRUE}


plot(dongfanghong.yearly.return, type = "l")
abline(h = 0, col = "red")
```

```{r, eval=TRUE}

ndiffs(dongfanghong.yearly.return)

```

```{r, fig.height=8, fig.width=10}

tsdisplay(dongfanghong.yearly.return)

```


```{r, eval=TRUE}
mean(dongfanghong.yearly.return)
sd(dongfanghong.yearly.return)

quantile(dongfanghong.yearly.return, c(0.05, seq(0,1,0.25)))

tail(dongfanghong.yearly.return, 2)

skewness(dongfanghong.yearly.return)
kurtosis(dongfanghong.yearly.return)
jarqueberaTest(dongfanghong.yearly.return)

Acf(dongfanghong.yearly.return)
```



